---
title: "R Notebook"
output: html_notebook
---

LOAD IN LIBRARIES
```{r}
install.packages("modelsummary")
install.packages("jtools")
install.packages("sjPlot")
install.packages("SciViews")

# Load in libraries
library(tidyverse)
library(ggplot2)
library(lubridate)
library(skimr)
library(psych)
library(Hmisc)
library(corrplot)
library(naniar)
library(GGally)
library(janitor)
library(modelsummary)
library(jtools)
library(sjPlot)
library(SciViews)

```

LOAD IN DATA SET(S)
```{r}
df <- read_csv("dataset.csv")
df_sales <- read_csv("sales_dataset.csv")

df %>% head()
df_sales %>% head()

```

PRELIM DATA CHECK
```{r}
df %>%
  gg_miss_var()

# Delete irrelevant variables
df %>% select(-EAtrading_volume, -EAprice) -> df

```


EDA


DESCRIPTIVES
```{r}
# Summary statistics

## DVs: news_volume, mean_sentiment_comments
df %>%
  select(news_volume, mean_sentiment_comments) %>%
  psych::describe()

## owned_tweets_about_games, paid_volume, press_release_volume
df %>%
  select(owned_tweets_about_games, paid_volume, press_release_volume) %>%
  psych::describe()

## trailer, launch, teaser, convention, expansions_dlc
df %>%
  select(trailer, launch, teaser, convention, expansions_dlc) %>%
  psych::describe()

```
 
CREATE NEW VARIABLES - PRE, DURING, POST LAUNCH PERIODS (CATEGORIES)
```{r}
# Select subset of data from 3 months pre-launch until 3 months post-launch (2018)
## May 10 2018 - December 28 2018
df %>%
  filter(
    row_number() >= 495 & row_number() <= 727
  ) -> df_2018

# Select subset of data from 3 months pre-launch until 3 months post-launch (2017)
## May 25 - December 29 2017
df %>%
  filter(
    row_number() >= 145 & row_number() <= 363
  ) -> df_2017


# Create new data frame for games across both years
df %>%
  filter(
    row_number() >= 145 & row_number() <= 727
  ) -> df_combo



# 2018 new date categories
## Pre-launch, during launch, post-launch
df_2018 %>%
  mutate(
    launch_period =
      case_when(
        (date >= "2018-05-10" & date <= "2018-08-09") ~ "Pre-Launch",
        (date >= "2018-08-10" & date <= "2018-09-28") ~ "During Launch",
        (date >= "2018-09-29" & date <= "2018-12-28") ~ "Post-Launch")
  ) -> df_2018

# 2017 new date categories
## Pre-launch, during launch, post-launch
df_2017 %>%
  mutate(
    launch_period =
      case_when(
        (date >= "2017-05-25" & date <= "2017-08-24") ~ "Pre-Launch",
        (date >= "2017-08-25" & date <= "2017-09-29") ~ "During Launch",
        (date >= "2017-09-30" & date <= "2017-12-29") ~ "Post-Launch")
  ) -> df_2017


# df_combo launch periods
## Pre-launch, during launch, post-launch - 2018
df_combo %>%
  mutate(
    launch_period =
      case_when(
        (date >= "2017-05-25" & date <= "2017-08-24") ~ "Pre-Launch",
        (date >= "2017-08-25" & date <= "2017-09-29") ~ "During Launch",
        (date >= "2017-09-30" & date <= "2017-12-29") ~ "Post-Launch",
        (date >= "2018-05-10" & date <= "2018-08-09") ~ "Pre-Launch",
        (date >= "2018-08-10" & date <= "2018-09-28") ~ "During Launch",
        (date >= "2018-09-29" & date <= "2018-12-28") ~ "Post-Launch")
  ) -> df_combo

```

DISTRIBUTIONS - 2018
```{r}
# news_volume, mean_sentiment_comments (grouped by launch period)
df_2018 %>%
  ggplot() + geom_histogram(aes(news_volume), fill = "#69b3a2", bins = 20) +
  facet_wrap(launch_period~., scales = "free") +
  theme_minimal()

df_2018 %>%
  ggplot() + geom_histogram(aes(mean_sentiment_comments), fill = "#69b3a2", bins = 20) + 
  facet_wrap(launch_period~., scales = "free") +
  theme_minimal()


# Bar chart - positive comments across each period
ggplot(df_2018, aes(x = df_2018$launch_period, y = df_2018$positive_comments)) + geom_bar(stat = "identity", fill = "#69b3a2") +
  labs(
    x = "Launch Period",
    y = "Number of Positive Comments") +
  theme_minimal() + coord_flip()

# Bar chart - negative comments across each period
ggplot(df_2018, aes(x = df_2018$launch_period, y = df_2018$negative_comments)) + geom_bar(stat = "identity", fill = "#69b3a2") +
  labs(
    x = "Launch Period",
    y = "Number of Negative Comments") +
  theme_minimal() + coord_flip()


# owned_tweets_about_games, paid_volume, press_release_volume
df_2018 %>%
  select(
    owned_tweets_about_games,
    paid_volume,
    press_release_volume,
    launch_period) %>%
  group_by(launch_period) %>%
  summarise_all(sum, na.rm=T) %>%
  pivot_longer(-launch_period, names_to = "variable", values_to = "volume") %>%
  ggplot(aes(x = variable, y = volume)) + geom_bar(stat = "identity", fill = "#69b3a2") + coord_flip() + 
  facet_wrap(launch_period~., scales = "free") + theme_minimal()

```

DISTRIBUTIONS - 2017
```{r}
# news_volume, mean_sentiment_comments (grouped by launch period)
df_2017 %>%
  ggplot() + geom_histogram(aes(news_volume), fill = "#DD6A60", bins = 20) +
  facet_wrap(launch_period~., scales = "free") +
  theme_minimal()

df_2017 %>%
  ggplot() + geom_histogram(aes(mean_sentiment_comments), fill = "#DD6A60", bins = 25) + 
  facet_wrap(launch_period~., scales = "free") +
  theme_minimal()

# Bar chart - positive comments across each period
ggplot(df_2017, aes(x = df_2017$launch_period, y = df_2017$positive_comments)) + geom_bar(stat = "identity", fill = "#DD6A60") +
  labs(
    x = "Launch Period - 2017",
    y = "Number of Positive Comments") +
  theme_minimal() + coord_flip()

ggplot(df_2017, aes(x = df_2017$launch_period, y = df_2017$negative_comments)) + geom_bar(stat = "identity", fill = "#DD6A60") +
  labs(
    x = "Launch Period - 2017",
    y = "Number of Negative Comments") +
  theme_minimal() + coord_flip()


# owned_tweets_about_games, paid_volume, press_release_volume
df_2017 %>%
  select(
    owned_tweets_about_games,
    paid_volume,
    press_release_volume,
    launch_period) %>%
  group_by(launch_period) %>%
  summarise_all(sum, na.rm=T) %>%
  pivot_longer(-launch_period, names_to = "variable", values_to = "volume") %>%
  ggplot(aes(x = variable, y = volume)) + geom_bar(stat = "identity", fill = "#DD6A60") + coord_flip() + 
  facet_wrap(launch_period~., scales = "free") + theme_minimal()
```

BAR CHARTS - OWNED & PAID TWEETS VOLUME BY YEAR
```{r}
# Temporarily rename variable names for bar chart output
df_2017 %>% rename(
  "Owned" = "owned_tweets_about_games",
  "Paid" = "paid_volume") -> df_2017

df_2018 %>% rename(
  "Owned" = "owned_tweets_about_games",
  "Paid" = "paid_volume") -> df_2018


# Bar chart: sums of owned tweets and paid tweets for 2017
df_2017 %>%
  select(
    Owned,
    Paid) %>%
  summarise_all(sum, na.rm = T) %>%
  pivot_longer(everything(), names_to = "Type", values_to = "Volume") %>%
  ggplot(aes(x = Type, y = Volume)) +
  geom_bar(stat = "identity", fill = "#73B9D5") +
  theme_minimal(base_size = 20)


# Bar chart: sums of owned tweets and paid tweets for 2018
df_2018 %>%
  select(
    Owned,
    Paid) %>%
  summarise_all(sum, na.rm = T) %>%
  pivot_longer(everything(), names_to = "Type", values_to = "Volume") %>%
  ggplot(aes(x = Type, y = Volume)) + geom_bar(stat = "identity", fill = "#3B3F40") +
  theme_minimal(base_size = 20)


# Change back variable names
df_2017 %>% rename(
  "owned_tweets_about_games" = "Owned",
  "paid_volume" = "Paid") -> df_2017

df_2018 %>% rename(
  "owned_tweets_about_games" = "Owned",
  "paid_volume" = "Paid") -> df_2018



```

CORRELATIONS CHECK - SPORTS GAMES 2018
```{r}
# Matrix 
df_2018 %>%
  select(
    news_volume,
    owned_tweets_about_games,
    owned_retweets_about_games,
    owned_favorites_about_games,
    paid_volume,
    paid_retweets,
    paid_favorites,
    earned_volume_comments
  ) %>%
  as.matrix %>% 
  rcorr() -> corr

corrplot(corr$r, method = "shade", order = "alphabet", type = "lower", addCoef.col = TRUE, tl.srt = 45, tl.pos = "ld")
```

CORRELATIONS CHECK - SPORTS GAMES 2017
```{r}
df_2017 %>%
  select(
    news_volume,
    owned_tweets_about_games,
    owned_retweets_about_games,
    owned_favorites_about_games,
    paid_volume,
    paid_retweets,
    paid_favorites,
    earned_volume_comments
  ) %>%
  as.matrix %>% 
  rcorr() -> corr2

corrplot(corr2$r, method = "shade", order = "alphabet", type = "lower", addCoef.col = TRUE, tl.srt = 45, tl.pos = "ld")
```

CORRELATIONS CHECK - KEY VARIABLES FULL DATA SET
```{r}
# Matrix 
df %>% select(-`...1`, -earnings) -> df

df %>%
  select(
    owned_tweets_about_games,
    owned_retweets_about_games,
    owned_favorites_about_games,
    paid_volume,
    paid_retweets,
    paid_favorites,
    paid_replies,
    earned_volume_comments,
    ups_comments,
    negative_comments,
    neutral_comments,
    positive_comments,
    mean_sentiment_comments,
    news_volume,
    press_release_volume,
    week) %>%
  as.matrix %>% 
  rcorr() -> corr_df

corrplot(corr_df$r, method = "shade", order = "alphabet", type = "lower", addCoef.col = TRUE, tl.srt = 45, tl.pos = "ld")
```

WRITE DATA FRAMES TO CSV FILES
```{r}
# Reformat data frames and write to CSV files
df_2017 %>% select(-`...1`) -> df_2017
df_2018 %>% select(-`...1`) -> df_2018

write.csv(df_2017, "/Users/angelchang/Desktop/VU/Master/P4/Advertising/Master Case/sports_2017.csv", row.names=FALSE)

write.csv(df_2018, "/Users/angelchang/Desktop/VU/Master/P4/Advertising/Master Case/sports_2018.csv", row.names=FALSE)
```



REGRESSIONS


DV - EARNED VOLUME COMMENTS (2017 & 2018)
```{r}
# 2017 
## Pre-Launch
df_2017 %>%
  filter(launch_period == "Pre-Launch") %>%
  lm(log1p(earned_volume_comments) ~ lag(log1p(paid_volume)) * lag(log1p(owned_tweets_about_games)),
     data = .) %>% #-> model_buzz
  summ(digits = 3)


# 2017 
## Post-Launch
df_2017 %>%
  filter(launch_period == "Post-Launch") %>%
  lm(log1p(earned_volume_comments) ~ lag(log1p(paid_volume)) * lag(log1p(owned_tweets_about_games)),
     data = .) %>%
  summ(digits = 3)


# 2018 
## Pre-launch
df_2018 %>%
  filter(launch_period == "Pre-Launch") %>%
  lm(log1p(earned_volume_comments) ~ lag(log1p(paid_volume)) * lag(log1p(owned_tweets_about_games)),
     data = .) %>% # -> model_buzz2
  summ(digits = 3)

# 2018 
## Post-launch
df_2018 %>%
  filter(launch_period == "Post-Launch") %>%
  lm(log1p(earned_volume_comments) ~ lag(log1p(paid_volume)) * lag(log1p(owned_tweets_about_games)),
     data = .) %>%
  summ(digits = 3)
```

VISUALIZING REGRESSION - PRE-LAUNCH 2017 BUZZ
```{r}
# IV - owned tweets
plot_model(model_buzz, type = "pred", terms = "owned_tweets_about_games") +
  theme_minimal(base_size = 18) +
  labs(
    title = "",
    x = "",
    y =""
  )

# IV - paid volume
plot_model(model_buzz, type = "pred", terms = "paid_volume") +
  theme_minimal(base_size = 18) +
  labs(
    title = "",
    x = "",
    y =""
  )
```

VISUALIZING REGRESSION - PRE-LAUNCH 2018 BUZZ
```{r}
# IV - owned tweets
plot_model(model_buzz2, type = "pred", terms = "owned_tweets_about_games") +
  theme_minimal(base_size = 18) +
  labs(
    title = "",
    x = "",
    y =""
  )

# IV - paid volume
plot_model(model_buzz2, type = "pred", terms = "paid_volume") +
  theme_minimal(base_size = 18) +
  labs(
    title = "",
    x = "",
    y =""
  )

  
```

TRADING PRICE, TRADING VOLUME
```{r}
# Combine 2018 and 2018 sports games data
all_df <- rbind(df_2017, df_2018)


# Trading price
model1 <- lm(EAprice ~ lag(launch_period), data = all_df)

all_df %>%
  lm(EAprice ~ lag(launch_period), data = .) %>%
  summ(digits = 3)

# Plot regression 1 visual
plot_model(model1, type = "pred", terms = "launch_period") +
  theme_minimal(base_size = 18) +
  labs(
    title = "",
    x = "",
    y =""
  )

# Trading volume
model2 <- lm(log(EAtrading_volume) ~ lag(launch_period), data = all_df)

# Plot regression 2 visual
plot_model(model2, type = "pred", terms = "launch_period") +
  theme_minimal(base_size = 18) +
  labs(
    title = "",
    x = "",
    y =""
  )


  
```



